---
title: "OS Survey - Quant Results"
author: "Linh Nguyen"
date: "3/23/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
---

# I. Meta-data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "asis")
options(digits = 2)
```

```{r, message=FALSE, warning=FALSE}
require(tidyverse)
require(rio)
require(summarytools)
require(likert)
require(xtable)
require(knitr)
sessionInfo()
```


# II. Preprocessing

## Data
```{r}
data <- rio::import(file = "../Data/cleaned.csv")
dict <- rio::import(file = "../Data/Dictionary.xlsx")
data$id <- as.character(data$id)

#data type demographics
data <- data %>% 
  mutate(age = factor(age, levels = c(1:7),
                         labels = c("18-22", "23-29", "30-39", "40-49", "50-59", "60-69", "70+")),
         continent = factor(continent, levels = c(1:6),
                            labels = c("Africa", "Asia", "Autralia/Oceania", "Europe", "North America", "South America")),
         group = factor(group, levels = c(1,2), labels = c("Flat rate", "Raffle")),
         gender_f = factor(gender_f, levels = c(1,2), labels = c("Female", "Male")),
         race_f = factor(race_f, levels = c(1:6),
                         labels = c("Asian", "Black", "Hispanic", "Native American", "Non-Hispanic White", "Mixed")),
         career = factor(career, levels = c(1:7),
                         labels = c("Undergraduate student", "Graduate student", "Post-doctoral fellow", 
                                    "Assistant professor/lecturer", "Associate/full professor", "Research scientist", "Other")))

#data type likert 
likert1 <- dict %>% 
  filter(value_label == "1 = It should never be used, 2 = It should only be used rarely, 3 = It should be used often, 4 = It should be used almost always") %>%
  pull(variable)
factor1 <- function(x){
  factor(x, levels = c(1:4), 
         labels = c("It should never be used", "It should only be used rarely", 
                    "It should be used often", "It should be used almost always"))
}

likert2 <- dict %>% 
  filter(value_label == "1 = Never, 2 = Once or Twice, 3 = Often") %>%
  pull(variable)
factor2 <- function(x){
  factor(x, levels = c(1:3), 
         labels = c("Never", "Once or Twice", "Often"))
}

likert3 <- dict %>% 
  filter(value_label == "1 = Never, 2 = Once, 3 = Occasionally, 4 = Frequently, 5 = Almost always") %>%
  pull(variable)
factor3 <- function(x){
  factor(x, levels = c(1:5), 
         labels = c("Never", "Once", "Occasionally", "Frequently", "Almost always"))
}

likert4 <- dict %>% 
  filter(value_label == "0 = No, 1 = Yes, 2 = I have not published an empirical paper") %>%
  pull(variable)
factor4 <- function(x){
  factor(x, levels = c(0:2), 
         labels = c("No", "Yes", "I have not published an empirical paper"))
}

data <- data %>% 
  mutate_at(likert1, factor1) %>% 
  mutate_at(likert2, factor2) %>% 
  mutate_at(likert3, factor3) %>% 
  mutate_at(likert4, factor4)

rm(likert1, likert2, likert3, likert4, factor1, factor2, factor3, factor4)

#list of ID with complete responses
full <- data %>% 
  filter(Finished == 1) %>% 
  pull(id)

#list of ID with correct attention checks
att <- data %>% 
  filter(attcheck == 1 & experience_19 == 1) %>% 
  pull(id)

#list of ID with complete AND correct attention checks
fullatt <- data %>% 
  filter(id %in% att & id %in% full) %>% 
  pull(id)
```

There are `r nrow(data)` participants in total, `r length(full)` of whom have completed responses and `r length(fullatt)` with completed responses who also passed the two attention checks.

# III. Demographics

### In entire dataset
```{r}
freq(data$age)
freq(data$gender_f)
freq(data$race_f)
freq(data$continent)
freq(data$career)
descr <- data %>% select(politics, c19stress, agree, consci, extra, neuro, open)
descr(descr, stats = "common", order = "p")
rm(descr)
```

### In complete dataset
```{r}
data %>% filter(id %in% full) %>% 
  freq(age)
data %>% filter(id %in% full) %>% 
  freq(gender_f)
data %>% filter(id %in% full) %>% 
  freq(race_f)
data %>% filter(id %in% full) %>% 
  freq(continent)
data %>% filter(id %in% full) %>% 
  freq(career)
```


# IV. Exploratory analyses

### 1. Questionable research practices

#### Self - Have you engaged in these practices?

```{r, results="hold"}
qrpself <- data.frame(var = dict %>% filter(scale == "Self QRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Self QRP") %>% pull(label))
likert <- data %>% select(all_of(qrpself$var))
colnames(likert) <- qrpself$labels
likert(likert)
```

- Grouped by gender

```{r}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)
plot(likert(likertf[,1:5], grouping = likertf$gender_f))
plot(likert(likertf[,6:10], grouping = likertf$gender_f))
```


#### Other - Percentage of researchers in ethnic minority/cultural psychology who you believe have engaged in these practices?

```{r}
qrppeer <- data.frame(var = dict %>% filter(scale == "Peer QRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Peer QRP") %>% pull(label))
descr <- data %>% select(all_of(qrppeer$var))
colnames(descr) <- qrppeer$labels
descr(descr, stats = "common", order = "p")
```

#### Opinion - What is your opinion of these practices?

```{r}
qrpopi <- data.frame(var = dict %>% filter(scale == "Opinion QRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Opinion QRP") %>% pull(label))
likert <- data %>% select(all_of(qrpopi$var))
colnames(likert) <- qrpopi$labels
likert(likert) %>% xtable() %>% print(type = "html")
```


### 2. Proposed Reforms to Research Practices

#### Awareness - Have you ever heard of these practices?

```{r}
prrpaware <- data.frame(var = dict %>% filter(scale == "Aware PRRP") %>% pull(variable),
                        labels = dict %>% filter(scale == "Aware PRRP") %>% pull(label))
descr <- data %>% select(all_of(prrpaware$var))
colnames(descr) <- prrpaware$labels
descr(descr, stats = "common", order = "p")
```

#### Self - Have you engaged in these practices?

```{r}
prrpself <- data.frame(var = dict %>% filter(scale == "Self PRRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Self PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrpself$var))
colnames(likert) <- prrpself$labels
likert(likert) %>% xtable() %>% print(type = "html")
```

#### Peer - Percentage of researchers in ethnic minority/cultural psychology who you believe have engaged in these practices?

```{r}
prrppeer <- data.frame(var = dict %>% filter(scale == "Peer PRRP") %>% pull(variable),
                       labels = dict %>% filter(scale == "Peer PRRP") %>% pull(label))
descr <- data %>% select(all_of(prrppeer$var))
colnames(descr) <- prrppeer$labels
descr(descr, stats = "common", order = "p")
```

#### Recent - Did you engage in these practices for your last empirical paper?

```{r}
prrprecent <- data.frame(var = dict %>% filter(scale == "Recent PRRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Recent PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrprecent$var))
colnames(likert) <- prrprecent$labels
likert(likert) %>% xtable() %>% print(type = "html")
```

#### Opinion - What is your opinion of these practices?

```{r}
prrpopi <- data.frame(var = dict %>% filter(scale == "Opinion PRRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Opinion PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrpopi$var))
colnames(likert) <- prrpopi$labels
likert(likert) %>% xtable() %>% print(type = "html")
```

#### Reasons - For not posting data

```{r}
whyinstr <- grep("^prrp1_5_", names(data), value = T)[-1]
descr <- data %>% filter (prrp1_4 == "No") %>% select(all_of(whyinstr))
colnames(descr) <-  c("Proprietary",
                      "Time-consuming",
                      "Scooping",
                      "Deidentification",
                      "Field not in favor",
                      "Already public",
                      "Mistake",
                      "Unfamiliar",
                      "Planning to",
                      "Others")
descr(descr, stats = "common", order = "p") %>% kable()
```



 
























