---
title: "OS Survey - Quant Results"
author: "Linh Nguyen"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
---

# I. Meta-data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "asis")
options(digits = 2)
```

```{r, message=FALSE, warning=FALSE, results = "hold"}
require(rio)
require(summarytools)
require(likert)
require(xtable)
require(knitr)
require(grid)
require(gridExtra)
require(sjPlot)
require(multcomp)
require(tidyverse)
require(viridis)
require(hrbrthemes)
sessionInfo()
```


# II. Preprocessing

## Data
```{r}
data <- rio::import(file = "../Data/cleaned.csv")
dict <- rio::import(file = "../Data/Dictionary.xlsx")
data$id <- as.character(data$id)

#data type demographics
data <- data %>% 
  mutate(age = factor(age, levels = c(1:7),
                         labels = c("18-22", "23-29", "30-39", "40-49", "50-59", "60-69", "70+")),
         continent = factor(continent, levels = c(1:6),
                            labels = c("Africa", "Asia", "Autralia/Oceania", "Europe", "North America", "South America")),
         group = factor(group, levels = c(1,2), labels = c("Flat rate", "Raffle")),
         gender_f = factor(gender_f, levels = c(1,2), labels = c("Female", "Male")),
         race_f = factor(race_f, levels = c(1:6),
                         labels = c("Asian", "Black", "Hispanic", "Native American", "Non-Hispanic White", "Mixed")),
         career = factor(career, levels = c(1:7),
                         labels = c("Undergraduate student", "Graduate student", "Post-doctoral fellow", 
                                    "Assistant professor/lecturer", "Associate/full professor", "Research scientist", "Other")))

#data type likert 
likert1 <- dict %>% 
  filter(value_label == "1 = It should never be used, 2 = It should only be used rarely, 3 = It should be used often, 4 = It should be used almost always") %>%
  pull(variable)
factor1 <- function(x){
  factor(x, levels = c(1:4), 
         labels = c("It should never be used", "It should only be used rarely", 
                    "It should be used often", "It should be used almost always"))
}

likert2 <- dict %>% 
  filter(value_label == "1 = Never, 2 = Once or Twice, 3 = Often") %>%
  pull(variable)
factor2 <- function(x){
  factor(x, levels = c(1:3), 
         labels = c("Never", "Once or Twice", "Often"))
}

likert3 <- dict %>% 
  filter(value_label == "1 = Never, 2 = Once, 3 = Occasionally, 4 = Frequently, 5 = Almost always") %>%
  pull(variable)
factor3 <- function(x){
  factor(x, levels = c(1:5), 
         labels = c("Never", "Once", "Occasionally", "Frequently", "Almost always"))
}

likert4 <- dict %>% 
  filter(value_label == "0 = No, 1 = Yes, 2 = I have not published an empirical paper") %>%
  pull(variable)
factor4 <- function(x){
  factor(x, levels = c(0:1), 
         labels = c("No", "Yes"))
}

likert5 <- dict %>% 
  filter(value_label == "0 = No, 1 = Yes") %>%
  pull(variable)
factor5 <- function(x){
  factor(x, levels = c(0:1), 
         labels = c("No", "Yes"))
}

data <- data %>% 
  mutate_at(likert1, factor1) %>% 
  mutate_at(likert2, factor2) %>% 
  mutate_at(likert3, factor3) %>% 
  mutate_at(likert4, factor4) %>% 
  mutate_at(likert5, factor5)

rm(likert1, likert2, likert3, likert4, likert5, 
   factor1, factor2, factor3, factor4, factor5)

#list of ID with complete responses
full <- data %>% 
  filter(Finished == 1) %>% 
  pull(id)

#list of ID with correct attention checks
att <- data %>% 
  filter(attcheck == 1 & experience_19 == 1) %>% 
  pull(id)

#list of ID with complete AND correct attention checks
fullatt <- data %>% 
  filter(id %in% att & id %in% full) %>% 
  pull(id)
```

There are `r nrow(data)` participants in total, `r length(full)` of whom have completed responses and `r length(fullatt)` with completed responses who also passed the two attention checks.

# III. Demographics

```{r}
freq(data$age)
freq(data$gender_f)
freq(data$race_f)
freq(data$continent)
freq(data$career)
freq(data$culture)
descr <- data %>% select(politics, c19stress, agree, consci, extra, neuro, open)
descr(descr, stats = "common", order = "p")
rm(descr)
```

# IV. Exploratory analyses

## 1. Questionable research practices

### 1a. Self
 
Have you engaged in these practices?

```{r, results="hold", fig.width = 10}
qrpself <- data.frame(var = dict %>% filter(scale == "Self QRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Self QRP") %>% pull(label))
likert <- data %>% select(all_of(qrpself$var))
colnames(likert) <- qrpself$labels
likert(likert)
plot(likert(likert[,1:10]))
```

#### Grouped by gender

```{r, fig.height = 10}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)

plot(likert(likertf[,1:10], grouping = likertf$gender_f))
```

```{r}
data <- data %>% 
  mutate(gender = ifelse(gender_f == "Female", 0, ifelse(gender_f == "Male", 1, NA)))
tab_model(lm(selfQRP ~ gender, data))
```

Overall, there does not seem to be a strong gender difference in engagement in questionable research practices. From the graphs of individual practices, we can see that female researchers reported more rounding of p-values whereas male researchers more often did not report problems of the studies. 

#### Grouped by age

```{r, results = "hold", fig.height = 15}
likert$age <- data$age
likerta <- likert %>% filter(is.na(age) == F)
plot(likert(likerta[,1:10], grouping = likerta$age))
```

```{r}
tab_model(lm(selfQRP ~ as.numeric(age), data))
```

Overall, there is no age difference in engagement in questionable research practices. Although it seems that the 70+ group has slightly different patterns compared to the rest, there are only 5 individuals in this age group.

#### Grouped by career stage

```{r, fig.height = 15}
likert$career <- data$career
likertc <- likert %>% filter(is.na(career) == F)
plot(likert(likertc[,1:10], grouping = likertc$career))
```

```{r}
data$careernum <- as.factor(as.numeric(data$career))
plot(glht(aov(selfQRP ~ careernum, data), linfct = mcp(careernum = "Tukey"), 
          alternative = "two.sided"),
     main = "Career stage")
```
Career stages:

- 2: Graduate student (N = 26)
- 3: Post-doctoral fellow (N = 20)
- 4: Assistant professor/lecturer (N = 76)
- 5: Associate/full professor (N = 120)
- 6: Research scientist (N = 7)
- 7: Other (N = 12)

Overall, there doesn't seem to be strong differences between different career stages in engagement in questionable research practices. Although it appears that research scientists and "other" career groups show a different pattern, it's important to note that there were only 19 participants (7.3%) that identified with these two groups. Graduate students reported less QRP engagement than assistant professors/lecturers and associate/full professors. Nonetheless, there were only 26 graduate students and many more professors/lecturers (`r 76+120`)

#### Grouped by leadership position

```{r, fig.height = 10}
likert <- likert %>% 
  mutate(lead_1 = data$lead_1,
         lead_2 = data$lead_2,
         lead_3 = data$lead_3)

likertl4 <- likert %>% filter(is.na(lead_1) == F &
                                is.na(lead_2) == F &
                                is.na(lead_3) == F)

likertl4 <- likertl4 %>%
  mutate(lead_any = ifelse(lead_1 == 0 & lead_2 == 0 & lead_3 == 0,
                           0, 1))

likertl4$lead_any <- factor(likertl4$lead_any, levels = c(0,1), labels = c("No leadership position",
                                                                           "Some leadership positions"))
plot(likert(likertl4[,1:10], grouping = likertl4$lead_any))

likert$lead_1 <- factor(data$lead_1, levels = c(0,1), labels = c("Not leader at own institution", "Leader at own institution"))
likertl1 <- likert %>% filter(is.na(lead_1) == F)
plot(likert(likertl1[,1:10], grouping = likertl1$lead_1))

likert$lead_2 <- factor(data$lead_2, levels = c(0,1), labels = c("Not leader at journal editorialship", "Leader at journal editorialship"))
likertl2 <- likert %>% filter(is.na(lead_2) == F)
plot(likert(likertl2[,1:10], grouping = likertl2$lead_2))

likert$lead_3 <- factor(data$lead_3, levels = c(0,1), labels = c("Not leader at professional societies", "Leader at professional societies"))
likertl3 <- likert %>% filter(is.na(lead_3) == F)
plot(likert(likertl3[,1:10], grouping = likertl3$lead_3))
```

Leadership positions: 

- Some leadership positions (N = `r count(likertl4[which(likertl4$lead_any == 'Some leadership positions'),])[[1]]`) vs. No leadership position (N = `r count(likertl4[which(likertl4$lead_any == 'No leadership position'),])[[1]]`)
- Leader at own institution (N = `r count(likert[which(likert$lead_1 == 'Leader at own institution'),])[[1]]`) vs. Not leader at own institution (N = `r count(likert[which(likert$lead_1 == 'Not leader at own institution'),])[[1]]`)
- Leader at journal editorialship (N = `r count(likert[which(likert$lead_2 == 'Leader at journal editorialship'),])[[1]]`) vs. Not leader at journal editorialship (N = `r count(likert[which(likert$lead_2 == 'Not leader at journal editorialship'),])[[1]]`)
- Leader at professional societies (N = `r count(likert[which(likert$lead_3 == 'Leader at professional societies'),])[[1]]`) vs. Not leader at professional societies (N = `r count(likert[which(likert$lead_3 == 'Not leader at professional societies'),])[[1]]`)

Overall there is no clear difference between researchers with and without recent leadership positions in their QRP engagement.

#### Grouped by identification with subfield of cultural/ethnic minority psychology

```{r, fig.height = 10}
likert$culture <- data$culture
likertce <- likert %>% filter(is.na(culture) == F)
plot(likert(likertce[,1:10], grouping = likertce$culture))
```

### 1b. Other

Percentage of researchers in ethnic minority/cultural psychology who you believe have engaged in these practices?

```{r, fig.height = 12, fig.width = 10, warning = F}
qrppeer <- data.frame(var = dict %>% filter(scale == "Peer QRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Peer QRP") %>% pull(label))
descr <- data %>% select(all_of(qrppeer$var))
colnames(descr) <- qrppeer$labels
descr(descr, stats = "common", order = "p")

# plot
descr$id <- as.character(1:nrow(descr))
descr <- gather(descr, key = "qrp", value = "percent",
                "Not reporting nonsignificance":"Imputing data")
p <- descr %>%
  ggplot( aes(x=qrp, y=percent, fill=qrp, color=qrp)) +
    geom_violin(width=1.25, size=0.2) +
    geom_boxplot(width = .15, fill = "white", color = "black") +
    stat_summary(fun.y=mean, geom="label", aes(label=round(..y.., 2), color = "black", size = 13, fill = "white")) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_minimal() +
    theme(
      legend.position="none",
      axis.text.y = element_text(size = 12)
    ) +
    coord_flip() + #horizontal version
    xlab("") +
    ylab("Percentage of researchers in ethnic minority/cultural psychology you believe have engaged in this")
print(p)
```

```{r, fig.height = 8, fig.width = 10}
#lollipop plot comparing with self engagement
descr <- data.frame(self = c(100-33, 100-56, 100-57, 100-43, 100-63, 100-74, 100-80, 100-42, 100-81, 100-93),
                    other = c(58.08, 48.52, 45.64, 52.29, 45.56, 35.53, 35.11, 49.73, 33.55, 20.48),
                    qrp = c("Not reporting nonsignificance", "Not reporting nonsignificance (covariate)",
                            "HARKing", "Not reporting alternative models", "Rounding p-value", 
                            "Excluding data", "Increasing sample", "Changing analysis",
                            "Not reporting problems", "Imputing data"))

descr <- descr %>% arrange(self) %>% 
  mutate(qrp = factor(qrp, qrp)) #factor is needed to preserve order

p <- ggplot(descr) +
  geom_segment(
    aes(x=qrp, xend=qrp, y=self, yend=other), 
    color= ifelse(descr$self < descr$other, "grey", "orange"), 
    size= ifelse(descr$self < descr$other, 1, 2)) +
  geom_point(
    aes(x=qrp, y=self),
    color="green", 
    size=4) +
  geom_point(
    aes(x=qrp, y=other),
    color="red", 
    size=4,
    shape=17) +
  theme_minimal() +
  coord_flip() +
  theme(
    axis.text.y = element_text(size = 12),
    axis.text.x = element_text(size = 12)
    ) +
  ylim(0, 80) +
  xlab("") +
  ylab("Percentage of researchers in ethnic minority/cultural psychology you believe have engaged in this")

p <- p + 
  annotate("text", x=grep("Changing analysis", descr$qrp), 20, 
           label="Underestimation of \n others' engagement", 
           color="orange", size=5 , angle=0, fontface="bold", hjust=0) +
  annotate("text", x=grep("Excluding data", descr$qrp), 50, 
           label="Overestimation of \n others' engagement", 
           color="gray", size=5 , angle=0, fontface="bold", hjust=0)

print(p)
```


### 1c. Opinion

What is your opinion of these practices?

```{r, results="hold"}
qrpopi <- data.frame(var = dict %>% filter(scale == "Opinion QRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Opinion QRP") %>% pull(label))
likert <- data %>% select(all_of(qrpopi$var))
colnames(likert) <- qrpopi$labels
likert(likert)
```

#### Grouped by gender

```{r}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)
plot(likert(likertf[,1:5], grouping = likertf$gender_f))
plot(likert(likertf[,6:10], grouping = likertf$gender_f))
```

#### Grouped by age

```{r}
likert$age <- data$age
likerta <- likert %>% filter(is.na(age) == F)
plot(likert(likerta[,1:2], grouping = likerta$age))
plot(likert(likerta[,3:4], grouping = likerta$age))
plot(likert(likerta[,5:6], grouping = likerta$age))
plot(likert(likerta[,7:8], grouping = likerta$age))
plot(likert(likerta[,9:10], grouping = likerta$age))
```

#### Grouped by career stage

```{r}
likert$career <- data$career
likertc <- likert %>% filter(is.na(career) == F)
plot(likert(likertc[,1:2], grouping = likertc$career))
plot(likert(likertc[,3:4], grouping = likertc$career))
plot(likert(likertc[,5:6], grouping = likertc$career))
plot(likert(likertc[,7:8], grouping = likertc$career))
plot(likert(likertc[,9:10], grouping = likertc$career))
```

#### Grouped by leadership position

```{r}
likert$lead_1 <- factor(data$lead_1, levels = c(0,1), labels = c("Not leader at own institution", "Leader at own institution"))
likertl1 <- likert %>% filter(is.na(lead_1) == F)
plot(likert(likertl1[,1:5], grouping = likertl1$lead_1))
plot(likert(likertl1[,6:10], grouping = likertl1$lead_1))

likert$lead_2 <- factor(data$lead_2, levels = c(0,1), labels = c("Not leader at journal editorialship", "Leader at journal editorialship"))
likertl2 <- likert %>% filter(is.na(lead_2) == F)
plot(likert(likertl2[,1:5], grouping = likertl2$lead_2))
plot(likert(likertl2[,6:10], grouping = likertl2$lead_2))

likert$lead_3 <- factor(data$lead_3, levels = c(0,1), labels = c("Not leader at professional societies", "Leader at professional societies"))
likertl3 <- likert %>% filter(is.na(lead_3) == F)
plot(likert(likertl3[,1:5], grouping = likertl3$lead_3))
plot(likert(likertl3[,6:10], grouping = likertl3$lead_3))
```

#### Group by identification with subfield of cultural/ethnic minority psychology

```{r}
likert$culture <- data$culture
likertce <- likert %>% filter(is.na(culture) == F)
plot(likert(likertce[,1:5], grouping = likertce$culture))
plot(likert(likertce[,6:10], grouping = likertce$culture))
```

## 2. Proposed Reforms to research practices

### 2a. Awareness

Have you ever heard of these practices?

```{r}
prrpaware <- data.frame(var = dict %>% filter(scale == "Aware PRRP") %>% pull(variable),
                        labels = dict %>% filter(scale == "Aware PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrpaware$var))
colnames(likert) <- prrpaware$labels
likert(likert)
```

#### Grouped by gender

```{r}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)
plot(likert(likertf[,1:3], grouping = likertf$gender_f))
```

#### Grouped by age

```{r}
likert$age <- data$age
likerta <- likert %>% filter(is.na(age) == F)
plot(likert(likerta[,1:3], grouping = likerta$age))
```

#### Grouped by career stage

```{r}
likert$career <- data$career
likertc <- likert %>% filter(is.na(career) == F)
plot(likert(likertc[,1:3], grouping = likertc$career))
```

#### Grouped by leadership position

```{r}
likert$lead_1 <- factor(data$lead_1, levels = c(0,1), labels = c("Not leader at own institution", "Leader at own institution"))
likertl1 <- likert %>% filter(is.na(lead_1) == F)
plot(likert(likertl1[,1:3], grouping = likertl1$lead_1))

likert$lead_2 <- factor(data$lead_2, levels = c(0,1), labels = c("Not leader at journal editorialship", "Leader at journal editorialship"))
likertl2 <- likert %>% filter(is.na(lead_2) == F)
plot(likert(likertl2[,1:3], grouping = likertl2$lead_2))

likert$lead_3 <- factor(data$lead_3, levels = c(0,1), labels = c("Not leader at professional societies", "Leader at professional societies"))
likertl3 <- likert %>% filter(is.na(lead_3) == F)
plot(likert(likertl3[,1:3], grouping = likertl3$lead_3))
```

#### Grouped by identification with subfield of cultural/ethnic minority psychology

```{r}
likert$culture <- data$culture
likertce <- likert %>% filter(is.na(culture) == F)
plot(likert(likertce[,1:3], grouping = likertce$culture))
```


### 2b. Self
 
Have you engaged in these practices?

```{r}
prrpself <- data.frame(var = dict %>% filter(scale == "Self PRRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Self PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrpself$var))
colnames(likert) <- prrpself$labels
likert(likert)
```

#### Grouped by gender

```{r}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)
plot(likert(likertf[,1:3], grouping = likertf$gender_f))
```

#### Grouped by age

```{r}
likert$age <- data$age
likerta <- likert %>% filter(is.na(age) == F)
plot(likert(likerta[,1:3], grouping = likerta$age))
```

#### Grouped by career stage

```{r}
likert$career <- data$career
likertc <- likert %>% filter(is.na(career) == F)
plot(likert(likertc[,1:3], grouping = likertc$career))
```

#### Grouped by leadership position

```{r}
likert$lead_1 <- factor(data$lead_1, levels = c(0,1), labels = c("Not leader at own institution", "Leader at own institution"))
likertl1 <- likert %>% filter(is.na(lead_1) == F)
plot(likert(likertl1[,1:3], grouping = likertl1$lead_1))

likert$lead_2 <- factor(data$lead_2, levels = c(0,1), labels = c("Not leader at journal editorialship", "Leader at journal editorialship"))
likertl2 <- likert %>% filter(is.na(lead_2) == F)
plot(likert(likertl2[,1:3], grouping = likertl2$lead_2))

likert$lead_3 <- factor(data$lead_3, levels = c(0,1), labels = c("Not leader at professional societies", "Leader at professional societies"))
likertl3 <- likert %>% filter(is.na(lead_3) == F)
plot(likert(likertl3[,1:3], grouping = likertl3$lead_3))
```

#### Grouped by identification with subfield of cultural/ethnic minority psychology

```{r}
likert$culture <- data$culture
likertce <- likert %>% filter(is.na(culture) == F)
plot(likert(likertce[,1:3], grouping = likertce$culture))
```


### 2c. Peer

Percentage of researchers in ethnic minority/cultural psychology who you believe have engaged in these practices?

```{r}
prrppeer <- data.frame(var = dict %>% filter(scale == "Peer PRRP") %>% pull(variable),
                       labels = dict %>% filter(scale == "Peer PRRP") %>% pull(label))
descr <- data %>% select(all_of(prrppeer$var))
colnames(descr) <- prrppeer$labels
descr(descr, stats = "common", order = "p")
```

### Recent - Did you engage in these practices for your last empirical paper?

```{r}
prrprecent <- data.frame(var = dict %>% filter(scale == "Recent PRRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Recent PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrprecent$var))
colnames(likert) <- prrprecent$labels
likert(likert)
```

#### Grouped by gender

```{r}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)
plot(likert(likertf[,1:3], grouping = likertf$gender_f))
```

#### Grouped by age

```{r}
likert$age <- data$age
likerta <- likert %>% filter(is.na(age) == F)
plot(likert(likerta[,1:3], grouping = likerta$age))
```

#### Grouped by career stage

```{r}
likert$career <- data$career
likertc <- likert %>% filter(is.na(career) == F)
plot(likert(likertc[,1:3], grouping = likertc$career))
```

#### Grouped by leadership position

```{r}
likert$lead_1 <- factor(data$lead_1, levels = c(0,1), labels = c("Not leader at own institution", "Leader at own institution"))
likertl1 <- likert %>% filter(is.na(lead_1) == F)
plot(likert(likertl1[,1:3], grouping = likertl1$lead_1))

likert$lead_2 <- factor(data$lead_2, levels = c(0,1), labels = c("Not leader at journal editorialship", "Leader at journal editorialship"))
likertl2 <- likert %>% filter(is.na(lead_2) == F)
plot(likert(likertl2[,1:3], grouping = likertl2$lead_2))

likert$lead_3 <- factor(data$lead_3, levels = c(0,1), labels = c("Not leader at professional societies", "Leader at professional societies"))
likertl3 <- likert %>% filter(is.na(lead_3) == F)
plot(likert(likertl3[,1:3], grouping = likertl3$lead_3))
```

#### Group by identification with subfield of cultural/ethnic minority psychology

```{r}
likert$culture <- data$culture
likertce <- likert %>% filter(is.na(culture) == F)
plot(likert(likertce[,1:3], grouping = likertce$culture))
```


### 2d. Opinion

What is your opinion of these practices?

```{r}
prrpopi <- data.frame(var = dict %>% filter(scale == "Opinion PRRP") %>% pull(variable),
                      labels = dict %>% filter(scale == "Opinion PRRP") %>% pull(label))
likert <- data %>% select(all_of(prrpopi$var))
colnames(likert) <- prrpopi$labels
likert(likert)
```

#### Grouped by gender

```{r}
likert$gender_f <- data$gender_f
likertf <- likert %>% filter(is.na(gender_f) == F)
plot(likert(likertf[,1:3], grouping = likertf$gender_f))
```

#### Grouped by age

```{r}
likert$age <- data$age
likerta <- likert %>% filter(is.na(age) == F)
plot(likert(likerta[,1:3], grouping = likerta$age))
```

#### Grouped by career stage

```{r}
likert$career <- data$career
likertc <- likert %>% filter(is.na(career) == F)
plot(likert(likertc[,1:3], grouping = likertc$career))
```

#### Grouped by leadership position

```{r}
likert$lead_1 <- factor(data$lead_1, levels = c(0,1), labels = c("Not leader at own institution", "Leader at own institution"))
likertl1 <- likert %>% filter(is.na(lead_1) == F)
plot(likert(likertl1[,1:3], grouping = likertl1$lead_1))

likert$lead_2 <- factor(data$lead_2, levels = c(0,1), labels = c("Not leader at journal editorialship", "Leader at journal editorialship"))
likertl2 <- likert %>% filter(is.na(lead_2) == F)
plot(likert(likertl2[,1:3], grouping = likertl2$lead_2))

likert$lead_3 <- factor(data$lead_3, levels = c(0,1), labels = c("Not leader at professional societies", "Leader at professional societies"))
likertl3 <- likert %>% filter(is.na(lead_3) == F)
plot(likert(likertl3[,1:3], grouping = likertl3$lead_3))
```

#### Group by identification with subfield of cultural/ethnic minority psychology

```{r}
likert$culture <- data$culture
likertce <- likert %>% filter(is.na(culture) == F)
plot(likert(likertce[,1:3], grouping = likertce$culture))
```


### 2e. Reasons

#### For not posting data

```{r}
whydata <- grep("^prrp1_5_", names(data), value = T)[-1]
descr <- data %>% filter (prrp1_4 == "No") %>% select(all_of(whydata))
colnames(descr) <-  c("Proprietary",
                      "Time-consuming",
                      "Scooping",
                      "Deidentification",
                      "Field not in favor",
                      "Already public",
                      "Mistake",
                      "Unfamiliar",
                      "Planning to",
                      "Others")
descr(descr, stats = "common", order = "p") %>% kable()
```

#### For not posting instruments

```{r}
whyinstr <- grep("^prrp2_5_", names(data), value = T)[-1]
descr <- data %>% filter (prrp2_4 == "No") %>% select(all_of(whyinstr))
colnames(descr) <-  c("Proprietary",
                      "Time-consuming",
                      "Scooping",
                      "Deidentification",
                      "Field not in favor",
                      "Already public",
                      "Unfamiliar",
                      "Planning to",
                      "Others")
descr(descr, stats = "common", order = "p") %>% kable()
```

#### For not preregistering

```{r}
whyprereg <- grep("^prrp3_5_", names(data), value = T)[-1]
descr <- data %>% filter (prrp3_4 == "No") %>% select(all_of(whyprereg))
colnames(descr) <-  c("Time-consuming",
                      "Scooping",
                      "Field not in favor",
                      "Already public",
                      "Unfamiliar",
                      "Others")
descr(descr, stats = "common", order = "p") %>% kable()
```

